Placeholder

### 2021-02-09 Paper_Histograms.Rmd
Added template code to combine age, gender, employ and ethnicity in two ways

```{r Plot age gender employ and ethnicity retro together}

@@

>>>>

```{r Add labels to gender retro and plot with gender and employ}

@@

```{r Tidy the ethnicity graphs}

#Graph 2
arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  theme(legend.position = "none") + 
  #theme(legend.title = element_blank()) +
  #geom_text(aes(label = n),
  #          size = 3,
  #          position = position_dodge(width=0.9), 
  #          vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))

#arranged_retro_ethnicity_plot <- plot_grid(arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white, labels = "")

```{r Plot age gender employ and ethnicity together}

ggarrange(arranged_retro_ethnicity_non_white,
          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
          nrow = 3,
          common.legend =  TRUE)

ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          common.legend = TRUE,
          ncol = 3,
          nrow = 2)
